Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-17 lloveras_2020.tex
alguna pabada
avanzando

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Runningheads
%
\runningauthor{D.G.~Lloveras~\etal}
%\runningtitle{}

@@

To study the global coronal 3D structure, SRT proved to be a powerful tool. Based on solar rotation, allow instruments to compile a time series of images that cover the entire corona.

@@

\diego{
A combination of the DEMT and global magnetic models has provided useful insight into the 3D thermodynamical structure of the global quiet-Sun corona. Recently \citet{lloveras_2017} combined DEMT whit coronal magnetic field of the global corona modeled by means of potential field source surface to study the last two solar minima.
 More recently, \citet{sachdeva_2019} compared the results of the latest version of the Alfvén Wave Solar Model (AWSoM) of the Space Weather Modeling Framework model with observations for the same rotations as this article in a globally fashion, obtaining good agreement up to 1 AU.
We used AWSoM results with two purposes. On the one hand to provide thermodynamic results to be contrasted with DEMT, and on the other hand to provide magnetohydrodynamic (MHD) coronal magnetic field model that is used to study thermodynamics along field lines.
}
We carry out a quantitatively detailed comparative \diego{DEMT/AWSoM} analysis of the Carrington Rotation (CR)-2082 during the Solar Cycle (SC) 23/24 minimum and CR-2208 during the declining fase of SC 24. To study CR-2082 data taken by the \textit{Extreme UltraViolet Imager Behind} (EUVI-B) on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) was used, while data taken by the \textit{Atmospheric Imaging Assembly instrument} (AIA), on board the \textit{Solar Dynamics Observatory} (SDO) mission was used to study CR-2208.

@@

{Several details from Figure \ref{perf_lat} are worth being highlighted. Firstly, for CR-2082 the electron density of both models agree within $\approx 20\%$ at all latitudes, and for CR-2208 the agreement is within $\approx5\%$. In the case of the electron temperature both models agree within $\approx 10-15\%$ at all latitudes for both target rotations. Secondly, for both target rotations, and for both models, these plots clearly show the relatively lower temperatures characterising the low-latitudes of the equatorial streamer belt compared to its mid-latitudes. Thirdly, for both target rotations, the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density. Note this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary. Last, note that the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend.}

@@

{For target rotation CR-2082, the median value of the electron density $\NCB$ of both models agree within $\approx 10-25\%$, depending of the type of leg, while the median value of the scale height $\lN$ agree within $\approx 10\%$. The leg-averaged electron temperature $\aTm$ of both models also agree within $10\%$. For target rotation CR-2208 the agreement of the median value of $\NCB$ and $\lN$ of both models is within $5\%$, while median values of $\aTm$ agree within $15\%$. These detailed results informed per magnetic structure are fully consistent with the large-scale comparison provided in Figure \ref{perf_lat}.}

@@

Results of the AWSoM model are compared to those of the DEMT reconstructions in the range of coronal heights $\approx 1.05-1.20\,\mrsun$ simultaneously covered by both models. In its current implementation, the AWSoM model can not reproduce down loops (type 0), so the comparison is restricted to type I, II and III field lines. The detailed comparison shown in this work can be summarized as follows. For CR-2082, the electron density of both models agree within $\approx 20\%$ in all regions, while for CR-2208 the agreement is within $\approx 5\%$. In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations. This level of agreement between both models is considerably better than that reported in previous works. \citet{oran_2015} and \citet{jin_2012} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.} \notebyalbert{Chip, if Section 2.2 explains the most significant improvements of AWSoM since the version used in those references, we can comment on the reason for the improvement here.}

{Within the quantitative match summarized in the previous paragraph, there are some qualitative agreements and disagreements between both models worth noticing. For both target rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes. On the other hand, while the latitude of the open/close magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary. Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), the AWSoM model shows the opposite trend. This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.} \notebyalbert{Chip: Even if the match AWSoM/DEMT is quantitatively pretty good, this qualitative opposite behavior is off putting. Do you think there is room for improvement in the AWSoM model here? Maybe worth mentioning?}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Runningheads
%
\runningauthor{D.G.~Lloveras~\etal}
\runningtitle{Comparative Coronal Study of CR-2082 and CR-2208}

@@

\diego{To study the global coronal 3D structure, SRT proved to be a powerful tool. Based on solar rotation, allow instruments to compile a time series of images that cover the entire corona collecting data from all lines of sight.}

@@

\diego{
A combination of the DEMT and global magnetic models has provided useful insight into the 3D thermodynamical structure of the global quiet-Sun corona. Recently \citet{lloveras_2017} combined DEMT whit coronal magnetic field of the global corona modeled by means of potential field source surface to study the last two solar minima.
}

\diego{DECIR ALGO DEL DESARROLLO DE AWSOM
More recently, \citet{sachdeva_2019} compared the results of the latest version of the Alfvén Wave Solar Model (AWSoM) of the Space Weather Modeling Framework model with observations for the same rotations as this article in a globally fashion, obtaining good agreement up to 1 AU.
We used AWSoM results with two purposes. On the one hand to provide thermodynamic results to be contrasted with DEMT, and on the other hand to provide magnetohydrodynamic (MHD) coronal magnetic field model that is used to study thermodynamics along field lines.
}
We carry out a quantitatively detailed comparative \diego{DEMT/AWSoM} analysis of the Carrington Rotation (CR)-2082 during the Solar Cycle (SC) 23/24 minimum and CR-2208 during the declining fase of SC 24. To study CR-2082 data taken by the \textit{Extreme UltraViolet Imager Behind} (EUVI-B) on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) was used, while data taken by the \textit{Atmospheric Imaging Assembly instrument} (AIA), on board the \textit{Solar Dynamics Observatory} (SDO) mission was used to study CR-2208.

@@

{{Several details from Figure \ref{perf_lat} are worth being highlighted. Firstly, at most latitudes the overal agreement of the electron density of both models is within $\approx 20\%$ for CR-2082, and $\approx 5\%$ for CR-2208. The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much. In the case of the electron temperature, for both target rotations the models agree within $\approx 15\%$ at all latitudes of the streamer belt, showing larger discrepancies in the CHs.} Secondly, for both target rotations, and for both models, these plots clearly show the relatively lower temperatures characterising the low-latitudes of the equatorial streamer belt compared to its mid-latitudes. Thirdly, for both target rotations, the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density. Note this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary. Last, note that the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend.}

@@

{For target rotation CR-2082, the median value of the electron density $\NCB$ of both models agree within $\approx 10-25\%$, {depending of the type of leg, with the largest discrepancy foud for legs of type II (near the open/closed boundary). The} median value of the scale height $\lN$ agree {within $\approx 10\%$ in all regions}. The leg-averaged electron temperature $\aTm$ of both models also agree {within $10\%$ in all regions}. For target rotation CR-2208 the agreement of the median value of $\NCB$ and $\lN$ of both models {is within $10\%$, while} median values of $\aTm$ agree within $15\%$. {These detailed results, being consistent with the large-scale comparison provided in Figure \ref{perf_lat}, show in detail how the AWSoM model performs compard to DEMT in different magetic strucures.}}

@@

Results of the AWSoM model are compared to those of the DEMT reconstructions in the range of coronal heights $\approx 1.05-1.20\,\mrsun$ simultaneously covered by both models. In its current implementation, the AWSoM model can not reproduce down loops (type 0), so the comparison is restricted to type I, II and III field lines. The detailed comparison shown in this work can be summarized as follows. For CR-2082, the electron density of both models agree within $\approx 20\%$ {in most regions}, while for CR-2208 the agreement is within $\approx 5\%$. {The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations{, with larger discrepancies in the CHs.} This level of agreement between both models is considerably better than that reported in previous works. \citet{oran_2015} and \citet{jin_2012} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.} \notebyalbert{Chip, if Section 2.2 explains the most significant improvements of AWSoM since the version used in those references, we can comment on the reason for the improvement here.}

{Within the quantitative match summarized in the previous paragraph, there are some qualitative agreements and disagreements between both models worth noticing. For both target rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes. On the other hand, while the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary. Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), the AWSoM model shows the opposite trend. This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.} \notebyalbert{Chip: Even if the match AWSoM/DEMT is quantitatively pretty good, this qualitative opposite behavior is off putting. Do you think there is room for improvement in the AWSoM model here? Maybe worth mentioning?}
